### 2024-12-04 paper/paper.qmd
organized entire project and added sketches, llm, and shiny app files

---
title: ""
author: 
  - Jerry Xia
thanks: "Code and data are available at: <>"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true 
bibliography: references.bib
---

>>>>

---
title: ""
author: 
  - Jerry Xia
thanks: "Code and data are available at: <https://github.com/Jerryx2020/TTC_Delay_Analysis>"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true 
bibliography: references.bib
---
